Are environmental and geographic variables effective surrogates for genetic variation in conservation planning?

### 2016-03-18 article/supporting_information.Rmd
+ bug fix in supp info

```{r, echo=FALSE}
knitr::kable(
	format.dataframe(
		ldply(
			seq_along(unique(spp.samples.DF$species)), 
			function(i) {
				data.frame(
					Species=paste0('\\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[i]),'}'),
					Primer=spp.BayeScan.sample.loci.subset.LST[[i]]@data@primers,
					Probability=spp.BayeScan.sample.loci.subset.LST[[i]]@results@summary[[2]],
					qval=spp.BayeScan.sample.loci.subset.LST[[i]]@results@summary[[4]],
					alpha=spp.BayeScan.sample.loci.subset.LST[[i]]@results@summary[[5]],
					fst=spp.BayeScan.sample.loci.subset.LST[[i]]@results@summary[[6]],
					Type=spp.BayeScan.sample.loci.subset.LST[[i]]@results@summary[[7]]
				)
			}
		),
		omit='Type'
	),
	digits=2,
	col.names=c('Species', 'Primer', 'Probability', 'q-value', '$\\alpha$', '$F_{ST}$', 'Type'),
	align=c('l', 'c', 'c', 'c', 'c', 'c', 'c'),
	caption='Loci classifications for each species. Each row denotes a sampled loci for a given species, and the evidence for it being under selection based on outputs from the program \\texttt{Bayescan}.'
)
```

>>>>

```{r, echo=FALSE}
knitr::kable(
	format.dataframe(
		ldply(
			seq_along(unique(spp.samples.DF$species)), 
			function(i) {
				if (!is.null(spp.BayeScan.sample.loci.subset.LST[[i]])) {
					data.frame(
						Species=paste0('\\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[i]),'}'),
						Primer=spp.BayeScan.sample.loci.subset.LST[[i]]@data@primers,
						Probability=spp.BayeScan.sample.loci.subset.LST[[i]]@results@summary[[2]],
						qval=spp.BayeScan.sample.loci.subset.LST[[i]]@results@summary[[4]],
						alpha=spp.BayeScan.sample.loci.subset.LST[[i]]@results@summary[[5]],
						fst=spp.BayeScan.sample.loci.subset.LST[[i]]@results@summary[[6]],
						Type=spp.BayeScan.sample.loci.subset.LST[[i]]@results@summary[[7]]
					)
				}
			}
		),
		omit='Type'
	),
	digits=2,
	col.names=c('Species', 'Primer', 'Probability', 'q-value', '$\\alpha$', '$F_{ST}$', 'Type'),
	align=c('l', 'c', 'c', 'c', 'c', 'c', 'c'),
	caption='Loci classifications for each species. Each row denotes a sampled loci for a given species, and the evidence for it being under selection based on outputs from the program \\texttt{Bayescan}. Note that loci in species with a single population were assumed to be neutral. Loci for these species do not appear in this table.'
)
```
